\documentclass[letterpaper]{article}

% --- Required Packages ---
\usepackage{parskip}            % Removes paragraph indentation, adds space between paragraphs
\usepackage[unicode, draft=false]{hyperref} % Setup hyperref package, and colours for links
\usepackage{titlesec}           % For custom section formatting
\usepackage{fancyhdr}           % Required for custom headers and footers
\usepackage{extramarks}         % Required for \lastxmark in the footer
\usepackage{enumitem}           % For nice lists (bullet points)

% --- Lab Details Variables ---
\newcommand{\labTitle}{Lab\ \#1}
\newcommand{\labDueDate}{April 9th, 2026}
\newcommand{\labClass}{CSC429}
\newcommand{\labClassTime}{}
\newcommand{\labClassInstructor}{Professor Fang}
\newcommand{\labAuthorName}{\textbf{Helen Huy, McCay Rudick, Jess Alencaster}}

% --- Basic Document Settings ---
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

% --- Header and Footer Settings ---
\pagestyle{fancy}
\lhead{\labAuthorName}
\rhead{\labClass\ (\labClassInstructor\ \labClassTime): \labTitle}
\lfoot{\lastxmark}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}

% --- Custom Section Formatting  ---
\titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}
\titleformat{\subsection}{\large\bfseries\raggedright}{}{0em}{}
\titlespacing{\subsection}{0pt}{8pt}{3pt}

\begin{document}
\thispagestyle{empty}

% --- Title Block ---

\vspace*{\fill}
\begin{center}
    {\Huge \scshape \labClass: \labTitle} \\ \vspace{10pt}
    {\Large \labAuthorName} \\ \vspace{5pt}
    {\large \labClassInstructor \ \labClassTime} \\ \vspace{5pt}
    {\large Due Date: \labDueDate}
\end{center} 
\vspace*{\fill}

\newpage

% BEGIN LAB CONTENT

\section{1. Open-Source Data Resources}

\subsection*{Resource 1: [Dataset Name]}
\textbf{Link:} \href{https://example.com}{https://example.com} \\
\textbf{Description:} Briefly describe the dataset here.

\subsection*{Resource 2: [Dataset Name]}
\textbf{Link:} \href{https://example.com}{https://example.com} \\
\textbf{Description:} Briefly describe the second dataset here.


\section{2. Open-Source ML Algorithms}

\subsection*{Classification: [Algorithm Name]}
\textbf{Link:} \href{https://example.com}{https://example.com} \\
\textbf{Description:} Briefly describe the algorithm and the platform you chose to use.

\subsection*{Regression: [Algorithm Name]}
\textbf{Link:} \href{https://example.com}{https://example.com} \\
\textbf{Description:} Briefly describe the algorithm and the platform.

\subsection*{Clustering: [Algorithm Name]}
\textbf{Link:} \href{https://example.com}{https://example.com} \\
\textbf{Description:} Briefly describe the algorithm and the platform.


\section{3. Security and Privacy Applications}

\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Application 1:} Describe the application briefly and explain why ML is useful for it. 
    \item \textbf{Application 2:} Describe the application briefly and explain why ML is useful for it.
    \item \textbf{Application 3:} Describe the application briefly and explain why ML is useful for it.
\end{itemize}


% --- References ---
\newpage
\section{References}

% We can do apa or smth later

\begin{enumerate}[leftmargin=2em]
    \item Author Last Name, First Initial. (Year). \textit{Title of the article or resource}. Website Name. \href{https://example.com}{https://example.com}
\end{enumerate}

\end{document}